Binary companions of red giant stars with APOGEE DR14

### 2018-02-22 paper/1-catalog/twoface-catalog.tex
Discussion words

\subsection{Comparison to previous work} \label{sec:compare-troup}

Stuff.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{unimodal.pdf}
\end{center}
\caption{%
\label{fig:troup-unimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{multimodal.pdf}
\end{center}
\caption{%
\label{fig:troup-multimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{data-changed.pdf}
\end{center}
\caption{%
\label{fig:troup-datachanged}
}
\end{figure}

>>>>

\subsection{Comparison to other APOGEE companion catalogs}
\label{sec:compare-troup}

There are at least two other recent catalogs of stellar systems and companions
based on \apogee\ data.

One of these studies focused on decomposing spectra of MS stars into mixtures of
stellar spectra (\citealt{El-Badry:2018}).
Conceptually, this method works because (a) for two unequal-mass stars,
unexpected absorption lines will appear superimposed on the brighter star's
spectrum, and (b) for close to equal-mass stars, the line depths and ratios will
not be well-matched by a single stellar model.
Using this technique, they identified thousands of candidate MS binaries and
trinaries, but did not consider giant stars ($\log g > 4$).
This sample is therefore complimentary to and non-overlapping with the catalog
presented in this work.

The other recent catalog searched for stellar and substellar companions to all
stars in \apogee\ \acronym{DR12} (including the RGB) that passed a series of
quality cuts, and had $\geq 8$ visits (\citealt{Troup:2016}).
For each star in the sample, orbits were fit to the visit RVs using a multi-step
orbit-fitting procedure: it starts by identifying significant periods and a few
harmonics of those periods, then fits a Keplerian orbit at each of these
harmonics using least-squares fitting (\citealt{De-Lee:2013}) with a modified
$\chi^2$ statistic that penalizes fits in which the phase coverage of the data
is poor.
This procedure is not guaranteed to provide a unique orbit solution.

Of the 382 companions released as a part of this previous search, only 188 of
the host stars passed the stellar parameter and quality cuts used to define the
parent sample in this work (see \sectionname~\ref{sec:data}).
We have looked at all of the overlapping stars to compare the previously derived
companion orbital properties to the posterior samplings derived with \thejoker.
We find that the comparisons fall in three categories:
(1) the parameters reported in \citet{Troup:2016} agree with the posterior
samplings, and the period distribution appears unimodal,
(2) the parameters reported in \citet{Troup:2016} identify one possible mode of
a likely multi-modal posterior pdf over orbital parameters, and
(3) the data changed significantly between \apogee\ \acronym{DR12} and \DR, so
no meaningful comparisons can be made; Roughly 1/3 of the comparison sample
falls into each class.
\figurename~\ref{fig:troup-unimodal} shows a few representative cases in which
the \citet{Troup:2016} orbital parameters (orbit shown as orange line in left
panels, parameters shown as orange + in right panels) is consistent with the
orbit samples from \thejoker.
\figurename~\ref{fig:troup-multimodal} shows a few representative cases in which
we find that the posterior pdf over orbital parameters is multimodal, and the
\citet{Troup:2016} orbit identifies one of these modes.
For completeness, \figurename~\ref{fig:troup-datachanged} shows two instances in
which the orbital parameters from \citet{Troup:2016} no longer make sense,
likely because the data changed between data releases.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{unimodal.pdf}
\end{center}
\caption{%
TODO:
\label{fig:troup-unimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{multimodal.pdf}
\end{center}
\caption{%
TODO:
\label{fig:troup-multimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{data-changed.pdf}
\end{center}
\caption{%
TODO:
\label{fig:troup-datachanged}
}
\end{figure}
